\textbf{Computational Fuzzy Extractors}

### 2013-05-21 CompFuzzExt.tex
rewording theorem 5.4

\begin{theorem}
\label{thm:lossless block sketch log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d) = O(\log n)$.  Let $\alpha \leq n/3$ and $m=(c+2d)n/d = O(n)$, and let $W$ be $m$-symbol fixing source over $\zo^{(m+\alpha)b}$.  If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/6$) using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
 there exists $\epsilon = \ngl(n)$ such that \consref{cons:informal construction} is a computational fuzzy extractor for $W$~(with key length $mb = \Hoo(W)$) that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$. The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.
\end{theorem}

>>>>

\begin{theorem}
\label{thm:lossless block sketch log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d) = O(\log n)$.  Let $\alpha \leq n/3$ and $m=(c+2d)n/d = O(n)$, and let $W$ be $m$-symbol fixing source over $\zo^{(m+\alpha)b}$.  If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/6$) using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
 there exists $\epsilon = \ngl(n)$ where \consref{cons:informal construction} is a computational fuzzy extractor for $W$~(with key length $mb = \Hoo(W)$, correcting $t$ errors) that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$. The generate procedure $\gen$ takes $O(n^2)$ operations over $\Fq$, and the reproduce procedure $\rep$ takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.
\end{theorem}
